quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-09-17 paper-quollr.Rmd
Initial work on adding notation table

>>>>

```{r notation-tb-html, eval=knitr::is_html_output()}
# Notation used in the paper

notation_df <- read_csv("misc/notation.csv")

notation_df |> 
  kable(caption = "Summary of notation for describing new methodology.") 
```

```{r notation-tb-pdf, eval=knitr::is_latex_output()}

notation_df <- read_csv("misc/notation.csv")

notation_df |> 
  kable(caption = "Summary of notation for describing new methodology.", booktabs = T) |>
  column_spec(1, width = "3cm") |>
  column_spec(2, width = "12cm")
```

### 2025-09-17 paper-quollr.tex
Initial work on adding notation table

>>>>

\begin{table}

\caption{\label{tab:notation-tb-pdf}Summary of notation for describing new methodology.}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{12cm}}
\toprule
Notation & Description\\
\midrule
\$n, p, k\$ & number of observations, variables, embedding dimension, respectively\\
\$\textbackslash{}mathbfit\{X\}, \textbackslash{}mathbfit\{x\}\$ & \$p\$-dimensional data (population, sample)\\
\$\textbackslash{}mathbfit\{y\}\$ & \$k\$-dimensional layout\\
\$P\$ & orthonormal basis, generating a \$d\textbackslash{}text\{-\}dimensional\$ linear projection of \$p\$-dimensional data\\
\$T\$ & true  model\\
\addlinespace
\$g\$ & functional mapping from \textbackslash{}pD\{\} to \textbackslash{}kD\{\}, especially as prescribed by NLDR\\
\$\textbackslash{}mathbfit\{\textbackslash{}theta\}\$ & (Hyper-) parameters for NLDR method\\
\$r\$ & ranges of the embedding components\\
\$C\textasciicircum{}\{(j)\}\$ & \$j\$-dimensional bin centers\\
\$(b\_1, b\_2)\$ & number of bins in each direction\\
\addlinespace
\$(a\_1, a\_2)\$ & binwidths, distance between centroids in each direction\\
\$(s\_1, \textbackslash{} s\_2)\$ & starting coordinates of the hexagonal grid\\
\$q\$ & buffer to ensure hexgrid covers data, proportion of data range, 0-1\\
\$m\$ & number of non-empty bins\\
\$b\$ & number of  hexagons in the grid\\
\addlinespace
\$h\$ & hexagonal id\\
\$l\$ & side length\\
\$A\$ & area\\
\$n\_h\$ & bin count\\
\$w\_h\$ & standardised bin counts\\
\bottomrule
\end{tabular}
\end{table}
